\documentclass[12pt]{report}
%\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\graphicspath{.}
\usepackage{fullpage}

\title{CSCE 315 \\ User Study}
\author{Oscar Reyes,\\
	James Corder Guy,\\
	Oleksandr Sofishchenko}
\date{April 26, 2017}

\begin{document}
	
	\maketitle
	
	\newpage
	
	\begin{center}
		\title{\textbf{Aggie Spirit Bus Route App}} \\
		
	\end{center}

	Our user study will consist of at least three people. We plan on having users answer a questionnaire with questions about the current Texas A\&M bus route app and also questions about our new implementation. The questions we will be asking are short and mainly about feedback. We do not have any quantitative data yet because we still need to set up the functionality of the website. The user study should take 25 minutes per person or if we do three people at the same time, we should be able to get it done in 45 minutes to an hour. In addition, we expect that we would spend anywhere from 10 minutes to an hour in other team's user studies.\\
	
	We plan on conducting the study outside of lab with another team. We plan to meet with another team on the weekend. Most likely on a Saturday at around 2:00 pm at the sixth floor of the annex. Their three members will participate in our user study and the three members of our team will participate in their user study. This would allow all of us to fulfill the requirements of the user study for each person and also each team.\\
	
	The Pre-Study questions we plan on asking the users are the following:\\
	1) First Name:\\
	2) Last Name:\\
	3) Do you use the bus transportation provided by the university?\\
	4) What do you dislike about the current TAMU bus route website/app?\\
	5) What do you like about the current TAMU bus route website/app?\\
	6) How often do you use the TAMU bus route website/app?\\
	7) What would you do to improve the the TAMU website/app?\\
	*** Names are being asked to keep record of which members of our class helped in our user study. If the person is not part of our class, then the name will not be saved.\\
	
	After the pre-study questions are done, we will have the user look at our website/app so they can try it out. We will have the students navigate through our website. We will make them try the buttons we have on the website, we will also have them use the map to see if the functionality of it is to their liking. All this should take about 20 minutes at most per person.\\
	
	The after study questions that we will ask the user are the following: \\
	1) What did you like about our current interface?\\
	2) What did you not like about our current interface?\\
	3) What would you do to make the website look more appealing to users?\\
	4) What additional features would you like in our to make it more useful for the user?\\
	5) Were the buttons that we had on the website self explanatory about what they were meant to do? \\
	6) If a button was not obvious to what it did, which was it? What did you think it did versus what it actually did?\\

\end{document}